\documentclass[margin,line]{res}
\usepackage{xcolor}
\usepackage{hyperref}
%\usepackage[colorlinks]{hyperref}
\hypersetup{
  colorlinks,
  %citecolor=violet,
  %linkcolor=red,
  urlcolor=blue}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{Xiaoyue Zhang \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
Koopmans Building, K 533     & {\it Tel:}  +31134662430 \\            
Department of EOR   &  {\it E-mail:}  x.zhang\_11@tilburguniversity.edu\\         
Tilburg University &{\it Web:} {\color{black} \url{www.xiaoyuezhang.net}} \\       
Warandelaan 2, 5037 AB Tilburg Netherlands  & \\     
\end{tabular}

\section{\sc Research Interests}
Development economics and empirical industrial organization

\section{\sc Education}
{\bf Tilburg University}, Tilburg, the Netherlands\\
%{\em Department of Econometrics and Operations Research} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. Candidate, Econometrics, 2023 (expected) 
\vspace*{.05in}
\item[] Supervisors:  Jaap H. Abbring, Christoph Walsh, Jeffrey R. Campbell
%\begin{list2}
%
%%\item Dissertation Topic:  ``Nonstationary Covariance Models for
%%  Spatial Data and Regression Problems'' 
%%\item Dissertation Topic:  ``Hierarchical Models for Multiple Ratings
%%  in Performance-Based\\ \hspace*{1.23in} Student Assessments.'' 
%
%\end{list2}
\vspace*{.05in}
\item[] Research Master in Economics,  September 2019
\end{list1}

{\bf London School of Economics and Political Science}, London, UK\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] M.Sc. in Econometrics and Mathematical Economics (Merit), 2016
\end{list1}

{\bf Johns Hopkins University}, Baltimore, USA\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] B.A. in Economics (with Honors, the Dean's list),  2015
\end{list1}

{\bf Wuhan University}, Wuhan, China\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] B.A. in Mathematics (with Honors, First-Class Scholarship),  2013
\end{list1}

\section{\sc Honors and Awards} 
Tilburg University: Jenny Ligthart Award, Best Research Master Student Continuing onto Ph.D., 2019

\vspace*{-2.5mm}
Tilburg University: Alumni Scholarship, 2019

\vspace*{-2.5mm}
Tilburg University: Koopmans Scholarship, 2018

%\vspace*{-2.5mm}
%London School of Economics and Political Science: graduated with Merit in Econometrics and Mathematical Economics, 2016
%
%\vspace*{-2.5mm}
%Johns Hopkins University: graduated with Honors in Economics, the Dean's list, 2015
%
%\vspace*{-2.5mm}
%Wuhan University: graduated with Honors in Mathematics, 2013
%
%\vspace*{-2.5mm}
%Wuhan University: First-Class Scholarship for Freshmen, 2010

\section{\sc Publications}
X. Zhang. ``An Analysis of the Rise and Fall of the Roman Empire.'' Emergence and Transfer of Wealth 02, no. 03 (2012): 39–47.
https://doi.org/10.12677/ETW.2012.23013.

\section{\sc Working \\ Papers}
X. Zhang and J. Xia. ``Will the average worker be left behind?'' Job market paper, \href{https://xyzhang9.github.io/papers/heterogeneousMarkupTFPGains.pdf}{\underline{draft}}.

X. Zhang. ``Optimal Subsidies for the Product Upgrading of Battery Electric Vehicles in China.'' \href{https://xyzhang9.github.io/presentation/cars.pdf}{\underline{Slides}}.

\section{\sc Work in \\ Progress}
``Varying Markups under Capital and Labor Distortions''

``Industrial Policies against Star Suppliers''

%\section{\sc Other Research}
%``Who Benefits From RMB Appreciation: China or America''  \hfill {\bf 2013}\\
%{\em Bachelor thesis, Wuhan University }
%\begin{list2}
%%\vspace*{.005in}
%\item The Chinese economy will slow down due to weak export industry, which may
%trigger restructure and reformation of the Chinese economy.
%\item Small manufacturers, labor unions, and agricultural producers in America will gain from RMB appreciation, while multinational companies who
%have factories in China will lose due to a rising production cost.
%\end{list2}
%
%``A Comparison Study of the Chinese Pension Fund System'' \hfill {\bf 2012}\\
%{\em  Funded undergraduate research project, Wuhan University }
%\begin{list2}
%%\vspace*{.005in}
%\item Compared the Chinese system with the US system, the UK system, and the German system to draw policy suggestions for the Chinese government.
%\end{list2}

\section{\sc Conference Presentations}
``Will the average worker be left behind?'' (circulated earlier as ``Misallocation under Heterogeneous Markups and Non-Constant Returns to Scale'')
Tilburg Structural Econometrics Group, the GSS seminar at Tilburg University, the IO seminar at KU Leuven, the ENTER Jamboree, China International Conference in Macroeconomics, the IAAE annual conference, the AMES China meeting, and China Center for Economic Research’s Summer Institute, the NSE International Annual Workshop, the EEA-ESEM summer meeting.  \hfill {\bf 2020-2022}
\vspace{-.3cm}\\

``Optimal Subsidies for the Product Upgrading of Battery Electric Vehicles in China.'' The virtual IO CEPR event.  \hfill {\bf 2022}
\vspace{-.3cm}\\

Discussant at the annual ENTER Jamboree at Universitat Aut\`onoma de Barcelona (cancelled) \hfill {\bf 2020}
\vspace{-.3cm}\\


``A Forgotten Bright Side: Technology Spillovers from SOEs Support
Industrial Upgrade.'' Workshop at Wuhan University \hfill {\bf 2019}

\section{\sc Teaching}
{\bf Tilburg University}, Tilburg, the Netherlands

\vspace{-.3cm}
Quantitative Methods \hfill {\bf 2019-2022}\\
{\em Teaching Assistant}\\
Taught tutorials of a research-master level course. 

\vspace{-.3cm}
Dynamic Economic Models \hfill {\bf 2019-2022}\\
{\em Teaching Assistant}\\
Taught labs of a master level course. Responsibility for answering students' questions, creating and grading assignments.  


{\bf Wuhan University}, Wuhan, China

\vspace{-.3cm}
{\em Instructor} \hfill {\bf 2019}\\
Taught a workshop on Git, Github, Jupyter Notebook, \LaTeX, and R Markdown.

\section{\sc Professional Experience}
{\bf CIECC}, Beijing, China

\vspace{-.3cm}
{\em Intern} \hfill {\bf 2017}\\
Studied the effectiveness of government subsidy on new energy vehicles. Collected and analyzed data on sales and R\&D expenditure. Used a simple OLS regression to show the correlations between policy changes and new energy vehicle companies’s sales and R\&D expenditure.

{\bf Capital Group}, Beijing, China

\vspace{-.3cm}
{\em Intern} \hfill {\bf 2013}\\
Researched and compared relevant water purification technologies. Suggested cooperation with Wuhan University to add a ultraviolet process. Initiated a business plan suggesting focusing on portable water purification devices according to current technological strengths and weaknesses.

\section{\sc Computer \\ Skills} 
Statistical software and computer language:  extensive use of R and MATLAB; some experience with SAS.\\
Applications: \LaTeX, Git, Jupyter Notebook, markdown, and presentation software.%\\
%Algorithms: Programming dynamic Markov decision game with heterogeneous agents
%\begin{list1}
%\item[] Statistical software and computer language:  extensive use of R and MATLAB; some experience with SAS.
%\item[] Applications: \LaTeX, Git, Jupyter Notebook, markdown, and presentation software.
%\item[] Algorithms: Programming dynamic Markov decision game with heterogeneous agents
%\end{list1}

\section{\sc Other \\ activities} 
Panelist for the re-accreditation and the NVAO assessment of the research master program at the Tinbergen Institute \hfill {\bf 2020}\\
Organizer of Tilburg Structural Econometrics Group \hfill {\bf 2021-2022}\\
Founder and organizer of Graduate Students' Society Book Club \hfill {\bf 2019-2022}\\

%\begin{list1}
%\item[] Panelist for the re-accreditation and the NVAO assessment of the research master program at the Tinbergen Institute (2020)
%\item[] Organizer of Tilburg Structural Econometric Group (2021-Present)
%\item[] Founder and organizer of Graduate Students' Society Book Club (2019-Present)
%\end{list1}

\section{\sc Languages} 
Native Chinese, fluent English, intermediate Dutch (CEFR: B1), intermediate French.

\section{\sc References}
Jaap H. Abbring, Christoph Walsh, Jeffrey R. Campbell

\end{resume}
\end{document}




